## NCAA Football Attendance 

Let's load the tidyverse.

```{r}
library(tidyverse)
```

And read in the attendance data:

```{r}
attendance <- read_csv("https://dwillis.github.io/sports-data-files/attendance.csv")
```

Using the tidyverse's `pivot_longer` function, turn the currently wide data into longer data and save it as a new dataframe called `attendance_longer`:

```{r}
attendance_longer <- attendance |> pivot_longer(cols = starts_with("20"), names_to = "Year", values_to = "Attendance")
```

Let's try to figure out whether football attendance has returned to "normal" by 2022, defining "normal" as 2019 figures. For that we'll need to isolate those two years using `filter()` and get rid of any NAs:

```{r}
attendance_two_years <- attendance_longer |> filter(Year == 2019 | Year == 2022) |> na.omit()
```

Now, in order to calculate a percentage change between those two years, we'll need to go back to wider data and again ditch teams where we don't have both years:

```{r}
attendance_wide <- attendance_two_years |> pivot_wider(names_from = Year, values_from = Attendance) |> na.omit()
```

Finally, we'll add a percentage change column to that dataframe (remember, it's (New-Old)/Old) and arrange it to see the results.

```{r}
attendance_wide <- attendance_wide |> mutate(percent = (`2022`-`2019`)/`2019` *100) |>
  arrange(desc(percent))
```

Some of these clearly are influenced by performance on the field. Below, describe the most interesting results (positive or negative) and what you think might be going on with them. Feel free to do some googling and describe what other data would be helpful to clarify what the best stories here might be. What surprises you about these results?

**ANSWER**

One of the most interesting results to me is that the top two schools with the biggest increase in attendance are from non-power five conferences. UTSA and East Carolina both had poor 2019 seasons before making the jump to good seasons in 2022, mainly providing the reason for the jump in attendance. Another interesting result to me is Arizona increasing its attendance over 30 percent, despite having just one more win in 2022 versus 2019. I think the main reasoning for that is they had been 1-16 in the two seasons in between, and so despite increasing from just 4 to 5 wins in 2019 to 2022, it had been a few years since frankly they were even watchable, and so those 5 wins felt like an enormous improvement. 

I think that getting data on the stadium capacities would be helpful for clarification. If a school had improved its stadium to increase seating or even got a new stadium between 2019-2022, that can be a reason as to why attendance increased. I also think that it would make it easier to find the best stories if the records for each of the seasons were alongside the rest of the data, because then you could pick out the schools that didn't increase their record by a lot, because there would almost certainly be outside factors as to why attendance increased.

The biggest thing that surprises me is that two SEC schools are in the top ten biggest increases in attendance. Given how big football matters in the south and in that conference, I would think that the percent change -- either way -- wouldn't change a whole lot.